\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\graphicspath{{./images}}
\title{ Designing and using a MySQL database for human resource management\\ Update 9}
\date{17 March 2022}
\author{Deepti Yadav\\ Roll No: 19111023 }
\begin{document}
\maketitle
\section*{Implementation}Implementation is the physical realization of database design And software
design. At this stage, the realization of the database Is achieved by using
Data Definition Language (DDL) from the Selected DBMS. Apart from the
database side, the creation of Graphical User Interface (GUI) is also done as
a form of Implementation in terms of its application.
\\
\section*{Data Conversion and Loading
}
Data Conversion and Loading is an activity to fill tables that Have been
made before with real company data . Data Conversion and Loading is a
mandatory activity so that the Database system can be used operationally
by the compay. Conversion here can mean changing the data format from
one Format to another so that it can be used in a new database system.
Company data itself can be retrieved from legacy systems or even Paperbased manual records. Including real data is somewhat Important, even if it
is still in the early stages of the process . Not Having them included from
the start may cause the developers to Modify everything they have built just
to make it compatible with The data .
\\
\section*{Testing}Testing is an activity to run a database system that is designed With the
aim of finding errors or errors that exist. With testing, the Designer prevents errors when the system has been used Operationally which results in
hampered the company’s daily Activities. In testing, the designer not only
directs attention to the Coding of the system but also the environment and
ambiance of the System. Before carrying out testing, the person responsible for Testing must understand the quality standards of what the test Intends
to do in order to achieve the appropriate testing results.
\\
\section*{Operational Maintenance} Operational Maintenance is the activity of monitoring Activities done within
the system in order to maintain the Performance of the system while the
business runs, as usual, using A database system that has been developed.
In addition to Maintaining the performance of the database system, it is
also Necessary to collect the requirements for the next Database System
Development Life Cycle.
\end{document}