\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\graphicspath{{./images}}
\title{ Designing and using a MySQL database for human resource management\\ Update 6}
\date{24 Feb 2022}
\author{Deepti Yadav\\ Roll No: 19111023 }
\begin{document}
\maketitle
\textbf{Continued....}
\\
According to a survey conducted by DB-Engines in May 2019, the Most
commonly used database management system is Oracle, MySQL, and Microsoft SQL Server. In accordance with the needs and business scale of the
Organization, MySQL is one of the best candidates to become a Database
management system from an employee database that will Be built and implemented. That’s because MySQL is not too Complex and sufficient for the
business scale of the organization Which consists of hundreds of employees,
unlike Oracle which is Very complex and is more aimed at companies with a
much larger Scale. Because the application to be built is also web-based, so
a Database that is suitable for use and in accordance with the scale of the
company the organization is MySQL. In addition to these Factors, MySQL
is very affordable compared to Oracle, where MySQL is a Database Management System (DBMS) that is free to Use and is licensed by the GNU
General Public License, while oracle is a paid DBMS (Express version can
be accessed free of Charge, but features -The DBMS features are limited and
only Recommended for educational and testing use).MySQL is a database
management system that is used through The web where MySQL operates
on a server .This provides a Good opportunity for writers to develop prototypes related Applications using a web base.
\section*{Database Life Cycle :-
}
In order to design a database that is usable in the long run, there Are a
few steps that should be followed. One of the most general And common
guidelines used is the Database Life Cycle. The steps Of the Database Life
Cycle are as follows.

\end{document}