\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\graphicspath{{./images}}
\title{ Designing and using a MySQL database for human resource management\\ Update 10}
\date{24 March 2022}
\author{Deepti Yadav\\ Roll No: 19111023 }
\begin{document}
\maketitle
\section*{Discussion}
After analyzing the ongoing business processes, there are Several problems
that can be corrected to reduce the losses Experienced by the company.
Some of these problems are: : Payroll costs are inflated because of fraud in
recording Attendance using only paper and pens without close Supervision.

\begin{itemize}
    \item The cost of paying overtime wages that are inflated due To fraud in
recording overtime duration.
\item The results of work that are not in accordance with the Cost of salaries
and overtime wages incurred (the progress Of the project undertaken is
not comparable with Statements of overtime and work from employees).
\item HRD employees have difficulty finding data that has long Been due to
manual archive storage without the existence Of a database that is a
centralized company data Analysis of business processes that run at the
company has Exposed the needs of the company which is a database
system for The management of the company’s workforce. From the
database System to be designed, the expectation of the organization is
that The database system can fulfill the following:
\begin{itemize}
    \item The database system can be the actual data storage Regarding employee attendance (with the help of Attendance machines). This
means that the database System can read data in the extension
format produced by The attendance machine.
\item The database system can help HRD employees in data Searching
so that data search can be done quickly and Accurately. This means that the database system must be Able to display the data
needed by HRD employees when HRD employees need them.
\item To accelerate the manual recording transition to database System usage, the user interface of the database Application that
is designed is expected to be user-friendly So that it is easy for
HRD employees to use to input and Pull data output. Based on
the problems and needs of the database system that Has been described above, the author can suggest a solution which Is making a
database system for the management of the Organization’s human
resource with the following explanation:
\end{itemize}
\item Creating a database for the organization which will be a Centralized data repository for all HRD operational Activities of the
organization such as employee personal Data collection, employee
attendance records, also the Calculation of salaries received by
employees.
\item Making a prototype of a web-based application that will Be a bridge
for users (HRD employees of the organization) To input data into the
database, process
\end{itemize}
\end{document}