\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\graphicspath{{./images}}
\title{ Designing and using a MySQL database for human resource management\\ Update 4}
\date{2 Feb 2022}
\author{Deepti Yadav\\ Roll No: 19111023 }
\begin{document}
\maketitle
\section*{introduction to database:-}
A database is an integrated collection of Data that is stored, managed and
centrally controlled. Databases Usually store information about entities in
large numbers (tens, Hundreds, to thousands of entities). Information stored
in the Database is the entity’s attributes (for example, name, price, and
Account balance) and the relationship of an entity with other Entities (for
example, which orders belong to which customers). The database has its
own language called query. There are several kinds of languages in the query
where the explanation is as follows:
\\
\begin{itemize}
    \item \textbf{Data Definition Language (DDL) :} Which is a language that Governs the making of structures from a database. DDL is Not related to
data that fills in the database structure. Some Examples of DDL are
CREATE, DROP, and ALTER.
\\
\item \textbf{Data Manipulation Language (DML) : } Which is a language That
governs changesto database contents. Some examples Of DML are
INSERT, UPDATE, DELETE, and SELECT.
\\
\item \textbf{Data Control Language (DCL) : } Which a language that Regulates
anyone who can access a part of the database Designed. Some examples
of DCL are GRANT and REVOKE.

\end{itemize}
\end{document}